Stage-Splitting a Modal Language

### 2014-10-28 paper/splitting.tex
additions to splitting section

%As with the dynamics, our stage-splitting algorithm for expressions in \lang\
%takes the form of two mutually-dependent judgments, $\splitonesym$ and
%$\splittwosym$, which respectively split terms that type $@ \bbone$ and $@
%\bbtwo$.  Before diving into the full generality, 
As discussed in the introduction, a stage splitter must take a term in \lang\
and produce two

\TODO waiting on how the intro defines splitting

In this section, we define splitting for partial values, then extend it to all
terms.

@@

The splitting rule for \texttt{mono} is more difficult.

>>>>

%As with the dynamics, our stage-splitting algorithm for expressions in \lang\
%takes the form of two mutually-dependent judgments, $\splitonesym$ and
%$\splittwosym$, which respectively split terms that type $@ \bbone$ and $@
%\bbtwo$.  Before diving into the full generality,

The goal of splitting is to take a multistage term and produce two new terms:
one with all of the stage \bbone\ content, and one with all of the stage \bbtwo\ content.
Exactly how this goal manifests depends on the form of the input. 
We consider four cases: stage \bbone\ values, stage \bbone\ terms, stage \bbtwo\ values,
and stage \bbtwo\ terms.

We cover stage \bbtwo\ value splitting first, because it is trivial by construction.
Since there is no stage \bbtwo\ expression that both is a value
and contains \bbone\ subexpressions, 
we say that stage \bbtwo\ values must contain no stage \bbone\ content.
Accordingly, there is nothing really to split.

@@

The splitting rule for \texttt{mono} is more difficult.
...
transition to dummy.

The evaluation rules for dummy values are given by:
\begin{mathpar}
\infer{e_1~e_2~\redsym~\mathtt{dummy}}{e_1~\redsym~\mathtt{dummy} & e_2~\redsym~v} \and
\infer{\unroll~e~\redsym~\mathtt{dummy}}{e~\redsym~\mathtt{dummy}}\and
\infer{\pio~e~\redsym~\mathtt{dummy}}{e~\redsym~\mathtt{dummy}}\and
\infer{\pit~e~\redsym~\mathtt{dummy}}{e~\redsym~\mathtt{dummy}}
\end{mathpar}

The basic idea here is that dummy will dynamically be whatever data structure you want it to be.

This is safe because [nico is just throwing something out here] 
it can only appear in the resumers of terms that have no circles in their \lang\ type.
Since the $\prev$ rule requires a circle type, dummy values cannot leak from
the resumers of stage \bbone\ terms into the resumers of stage \bbtwo\ terms.
